---
title: "Meta-Analysis"
author: "Olivia Cody"
date: "1/30/2018"
output:
  pdf_document: default
  html_document: default
---

Next steps:
- selection modeling - retrieve cell means ($par) and p-values (hession)
  - see code in meta-showdown and see how Felix did it
- TryCatch(), parallelize? to handel falures of convergance 
  - purrr for vectorizing 

Parameters would be:
- B1, b2, b3
   - Ggplot: x= b1, b2, b3; y = obs value; jitter; shape = est (naïve, additive PET, interactive pet; error bar = quantile 

- Get parameters and p-values in weightfun
  - look at metashowdown on get up
  - better at recovering moderators?
  
- mising value or trycatch()

- mutate(dataset(testset), me = d - D, rmse = sqrt((d-D)^2))


####*Techniques for detecting and adjusting bias*
**Ways to detect bias**
- Funnel plots
- Forest plots?
- Egger Test (looks at slope)

**Ways to detect and adjust bias**
- Trim and fill
- PET (just looks at intercept) and PEESE
- P-curve
- P-uniform

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(MASS)
library(tidyverse)
library(truncnorm)
library(truncdist)
library(pwr)
library(compiler)
library(metafor)
library(ggplot2)

# load study-simulating functions
source("sim-studies/sim-studies.R", chdir=TRUE)
# example data set for testing & debugging
load("sim.Rdata")

```

*k* the number of studies in the MA
*delta* the true effect (or the average of the true effects if heterogeneity exists)
*tau* the SD around the true effect
*empN* a logical, whether to use the empirical per-group N distribution
*maxN* the max possible group size that could be created *this needs to be set higher than what can actually be generated--it doesn't mean you get bigger samples
*minN* the min of the truncated normal for sample size
*meanN* the average of the truncated normal for sample size

*selProp* the proportion of the sample affected by bias
*qrpEnv* the qrp environment that produced the literature: 'none', 'low', 'med', 'high'
*empN.boost* A constant that is added to the empirical effect sizes

####*Example*
```{r}
ggplot(diamonds, aes(x = carat, y = price, col = color) +
       geom_point() + #plots stuff
         facet_wrap(~color) + #separtest into plots
         geom_smooth() + #(#can use aes(group = color)to tell it to group by specific type for the line) + #defalt is weighted moving average, can spesific like method = "lm" 
         scale_x_continuous("Estimate (d)", breaks = c(-0.3, 0, 0.3, 0.6, 0.9))) 
       

#get random sample from dataset
mydiam = diamonds %>% 
  sample_n(5000)
summary(diamonds)
ggplot(diamonds, aes(x = carat, y = price, col = color) + 
         geom_point())
```
####*Code that does it all in one*
```{r}

# Function that runs dataMA three times + fake data
modMA <- function(k, selProp = 0, qrpEnv = "none", empN.boost = 0) {
  d1 <- dataMA(k = k, delta = .2, tau = 0, 
               empN = 0, maxN = 200, minN = 20, meanN = 50, 
               selProp = selProp, qrpEnv = qrpEnv, empN.boost = empN.boost)
  d2 <- dataMA(k = k, delta = .5, tau = 0, 
               empN = 0, maxN = 200, minN = 20, meanN = 50, 
               selProp = selProp, qrpEnv = qrpEnv, empN.boost = empN.boost)
  d3 <- dataMA(k = k, delta = .8, tau = 0, 
               empN = 0, maxN = 200, minN = 20, meanN = 50, 
               selProp = selProp, qrpEnv = qrpEnv, empN.boost = empN.boost)
  return(bind_rows(data.frame(d1), data.frame(d2), data.frame(d3), .id = "id"))
}


# function to analyze results of dataMA
inspectMA <- function(dataset) {
  # basic model
  rmamod <- rma(yi = d, sei = se, data = dataset)
  # test for moderator
  moderation.test <- rma(yi = d, sei = se, 
                         mods = ~id, data = dataset)
  # test for small-study effect
  egger.PET.test <- rma(yi = d, sei = se,
                    mods = ~se, data = dataset)
  # test for moderator after adjustment for small-study
  joint.test.additive <- rma(yi = d, sei = se,
                    mods = ~id + se, data = dataset)
  joint.test.interactive <- rma(yi = d, sei = se,
                             mods = ~id * se, data = dataset)
  # not sure how to interpret these parameters in the interactive model
  # test for moderator in hedges & vevea weight model
  # return test results
  out = data.frame(d.obs = summary(rmamod)$b[1],
                    se.obs = summary(rmamod)$se[1],
                    d.p = summary(rmamod)$pval[1],
                    # Moderators
                    # Note that .1 is the intercept, reference group
                    mod.b.obs.1 = summary(moderation.test)$b[1],
                    mod.b.obs.2 = summary(moderation.test)$b[2],
                    mod.b.obs.3 = summary(moderation.test)$b[3],
                    mod.p.1 = summary(moderation.test)$pval[1],
                    mod.p.2 = summary(moderation.test)$pval[2],
                    mod.p.3 = summary(moderation.test)$pval[3],
                    # Egger / PET
                    d.obs.pet = summary(egger.PET.test)$b[1],
                    p.pet = summary(egger.PET.test)$pval[1],
                    b.egger = summary(egger.PET.test)$b[2],
                    p.egger = summary(egger.PET.test)$pval[2],
                    # joint PET-RMA tests
                    #Additive model 
                    joint.add.b1 = summary(joint.test.additive)$b[1],
                    joint.add.b2 = summary(joint.test.additive)$b[2],
                    joint.add.b3 = summary(joint.test.additive)$b[3],
                    joint.add.b.egger = summary(joint.test.additive)$b[4],
                    joint.add.p1 = summary(joint.test.additive)$pval[1],
                    joint.add.p2 = summary(joint.test.additive)$pval[2],
                    joint.add.p3 = summary(joint.test.additive)$pval[3],
                    joint.add.p.egger = summary(joint.test.additive)$pval[4],
                    #Interactive model
                    joint.inter.b1 = summary(joint.test.interactive)$b[1],
                    joint.inter.b2 = summary(joint.test.interactive)$b[2],
                    joint.inter.b3 = summary(joint.test.interactive)$b[3],
                    joint.inter.b1.egger = summary(joint.test.interactive)$b[4],
                    joint.inter.b2.egger = summary(joint.test.interactive)$b[5],
                    joint.inter.b3.egger = summary(joint.test.interactive)$b[6],
                    joint.inter.p1 = summary(joint.test.interactive)$pval[1],
                    joint.inter.p2 = summary(joint.test.interactive)$pval[2],
                    joint.inter.p3 = summary(joint.test.interactive)$pval[3],
                    joint.inter.p1.egger = summary(joint.test.interactive)$pval[4],
                    joint.inter.p2.egger = summary(joint.test.interactive)$pval[5],
                    joint.inter.p3.egger = summary(joint.test.interactive)$pval[6]
                    )
  return(data.frame(out))
  }



# function to make various visuals of MA: (?)

visualizeMA <- function(dataset)



theme_poster <- theme(text = element_text(size = 32),
                      legend.position = "none")

temp <- bind_rows(noBias = res.nobias, 
                  bias = res.medPB.hiQRP, 
                  .id = "id") %>% 
  select(id,
         mod.obs.b1:mod.obs.b3, 
         joint.add.b1:joint.add.b3, 
         joint.inter.b1:joint.inter.b3) %>% 
  gather(key = "key", value = "value", mod.obs.b1:joint.inter.b3) %>% 
  separate(key, into = c("junk", "estimator", "coefficient"), sep = "\\.") %>% 
  # augment with true values & fix factor order
  mutate(delta = ifelse(coefficient == "b1", 0,
                        ifelse(coefficient == "b2", 0.3, 0.6)),
         rmse = sqrt((value - delta)^2),
         id = fct_relevel(id, c("noBias", "bias")),
         estimator = fct_relevel(estimator, c("obs", "add", "inter")))

temp2 <- bind_rows(noBias = res.smallfx.nobias, 
                  bias = res.smallfx.medPB.hiQRP, 
                  .id = "id") %>% 
  select(id,
         mod.obs.b1:mod.obs.b3, 
         joint.add.b1:joint.add.b3, 
         joint.inter.b1:joint.inter.b3) %>% 
  gather(key = "key", value = "value", mod.obs.b1:joint.inter.b3) %>% 
  separate(key, into = c("junk", "estimator", "coefficient"), sep = "\\.") %>% 
  # augment with true values
  mutate(delta = ifelse(coefficient == "b1", 0,
                        ifelse(coefficient == "b2", 0.2, 0.4)),
         rmse = sqrt((value - delta)^2),
         id = fct_relevel(id, c("noBias", "bias")),
         estimator = fct_relevel(estimator, c("obs", "add", "inter")))

# plot means
temp %>% 
  group_by(id, estimator, coefficient, delta) %>% 
  summarize(m = mean(value),
            q.lower = quantile(value, .025),
            q.upper = quantile(value, .975)) %>% 
  ggplot(aes(x = coefficient, y = m, shape = estimator)) +
  geom_hline(aes(yintercept = delta), col = 'grey25') +
  geom_pointrange(aes(ymin = q.lower, ymax = q.upper),
                  size = 2, position = position_dodge(width = .5)) +
  facet_grid(~id) +
  scale_y_continuous("Estimate (d)",
                     breaks = c(-0.3, 0, 0.3, 0.6, 0.9)) +
  theme_poster
ggsave("me_bigfx.png", width = 10.25, height = 4)

temp2 %>% 
  group_by(id, estimator, coefficient, delta) %>% 
  summarize(m = mean(value),
            q.lower = quantile(value, .025),
            q.upper = quantile(value, .975)) %>% 
  ggplot(aes(x = coefficient, y = m, shape = estimator)) +
  geom_hline(aes(yintercept = delta), col = 'grey25') +
  geom_pointrange(aes(ymin = q.lower, ymax = q.upper),
                  size = 2, position = position_dodge(width = .5)) +
  facet_grid(~id) +
  scale_y_continuous("Estimate (d)",
                     breaks = c(-0.4, -0.2, 0, 0.2, 0.4, 0.6, 0.8)) +
  theme_poster
ggsave("me_smfx.png", width = 10.25, height = 4)


# plot RMSE
temp %>% 
  group_by(id, estimator, coefficient) %>% 
  summarize(m = mean(rmse),
            q.lower = quantile(rmse, .025),
            q.upper = quantile(rmse, .975)) %>% 
  ggplot(aes(x = coefficient, y = m, shape = estimator,
             ymin = q.lower, ymax = q.upper)) +
  geom_pointrange(size = 2, position = position_dodge(width = .5)) +
  facet_wrap(~id) +
  scale_y_continuous("RMSE") +
  theme_poster
ggsave("rmse_bigfx.png", width = 10.25, height = 4)

temp2 %>% 
  group_by(id, estimator, coefficient) %>% 
  summarize(m = mean(rmse),
            q.lower = quantile(rmse, .025),
            q.upper = quantile(rmse, .975)) %>% 
  ggplot(aes(x = coefficient, y = m, shape = estimator,
             ymin = q.lower, ymax = q.upper)) +
  geom_pointrange(size = 2, position = position_dodge(width = .5)) +
  facet_wrap(~id) +
  scale_y_continuous("RMSE") +
  theme_poster
ggsave("rmse_smfx.png", width = 10.25, height = 4)

# Power / Type I
temp.p <- bind_rows(noBias = res.nobias, 
                    bias = res.medPB.hiQRP, 
                    .id = "id") %>% 
  select(id,
         mod.p1:mod.p3, 
         joint.add.p1:joint.add.p3, 
         joint.inter.p1:joint.inter.p3) %>% 
  gather(key = "key", value = "value", mod.p1:joint.inter.p3) %>% 
  separate(key, into = c("junk", "estimator", "coefficient"), sep = "\\.",
           # need fill = "left" to deal with shorter "mod.p1" vs "joint.add.p1"
           fill = "left") %>% 
  mutate(id = fct_relevel(id, "noBias", "bias"),
         estimator = fct_relevel(estimator, c("mod", "add", "inter")))

temp.p2 <- bind_rows(noBias = res.smallfx.nobias, 
                    bias = res.smallfx.medPB.hiQRP, 
                    .id = "id") %>% 
  select(id,
         mod.p1:mod.p3, 
         joint.add.p1:joint.add.p3, 
         joint.inter.p1:joint.inter.p3) %>% 
  gather(key = "key", value = "value", mod.p1:joint.inter.p3) %>% 
  separate(key, into = c("junk", "estimator", "coefficient"), sep = "\\.",
           # need fill = "left" to deal with shorter "mod.p1" vs "joint.add.p1"
           fill = "left") %>% 
  mutate(id = fct_relevel(id, "noBias", "bias"),
         estimator = fct_relevel(estimator, c("mod", "add", "inter")))

temp.p %>% 
  group_by(id, estimator, coefficient) %>% 
  summarize(sig = mean(value < .05)) %>% 
  ggplot(aes(x = coefficient, y = sig, 
             shape = interaction(estimator, id),
             group = estimator)) +
  geom_point(size = 5, position = position_dodge(width = .5)) +
  scale_shape_manual(values = c(16, 17, 15, 1, 2, 0)) +
  theme_poster
ggsave("nhst_bigfx.png", width = 6, height = 4)

temp.p2 %>% 
  group_by(id, estimator, coefficient) %>% 
  summarize(sig = mean(value < .05)) %>% 
  ggplot(aes(x = coefficient, y = sig, 
             shape = interaction(estimator, id),
             group = estimator)) +
  geom_point(size = 5, position = position_dodge(width = .5)) +
  scale_shape_manual(values = c(16, 17, 15, 1, 2, 0)) +
  theme_poster
ggsave("nhst_smfx.png", width = 6, height = 4)

# temp.p2 %>% 
#   group_by(id, estimator, coefficient) %>% 
#   summarize(sig = mean(value < .05)) %>% 
#   ggplot(aes(x = coefficient, y = sig, shape = estimator)) +
#   geom_point(size = 3, position = position_dodge(width = .5)) +
#   facet_wrap(~id)





# approach 2: scatterpoints
# Looks too muddy
# temp %>% 
#   group_by(id, estimator, coefficient, delta) %>% 
#   ggplot(aes(x = coefficient, y = value, shape = estimator)) +
#   geom_boxplot(position = position_dodge(width = .5)) +
#   geom_jitter(alpha = .5,
#               position = position_jitterdodge(dodge.width = .5, jitter.width = .25)) +
#   facet_grid(~id) +
#   geom_point(aes(y = delta), col = 'darkred', size = 2) +
#   scale_y_continuous(breaks = c(-0.3, 0, 0.3, 0.6, 0.9))
#________________________________________________________________________________


# Function for extracting selection model results as tidy table
tidy_psm <- function(x) {
  # get coefficients
  b <- x[[2]]$par
  # get SEs as the sqrt of the inverse of the hessian
  se.psm <- diag(sqrt(solve(x[[2]]$hessian)))
  # make row names
  # Get moderator names
  mods <- colnames(x$XX)[-1]
  # Get selection steps
  steps <- NULL
  for (i in 2:length(x$steps)) {
    steps <- c(steps, paste0(x$steps[i-1], "<p<", x$steps[i]))
  }
  term = c("variance", "intrcpt", mods, steps)
  # make a data frame
  out <- data.frame(term, b = b, se = se.psm) %>% 
    # add z-scores, p-vals, CIs
    mutate(z = b/se,
           p = 2*pnorm(abs(z), lower.tail = F),
           ci.lb = b - 1.96*se,
           ci.ub = b + 1.96*se)
  return(out)
}


#work space below:

#point estimate out like this:
mod <- with(data, weightfunct(d, v))
b <- mod[[2]]$par

#I suspect getting a standard error, confidence interval, p-value, etc. will require using the Hessian matrix stored at mod[[2]]$hessian. Feel like researching this?

```

####*Function output documentation*
##**dataMA**
*k* the number of studies in the MA
*delta* the true effect (or the average of the true effects if heterogeneity exists)
*tau* the SD around the true effect
*empN* a logical, whether to use the empirical per-group N distribution
*maxN* the max possible group size that could be created *this needs to be set higher than what can actually be generated--it doesn't mean you get bigger samples
*minN* the min of the truncated normal for sample size
*meanN* the average of the truncated normal for sample size
*selProp* the proportion of the sample affected by bias
*qrpEnv* the qrp environment that produced the literature: 'none', 'low', 'med', 'high'
*empN.boost* A constant that is added to the empirical effect sizes

*d* effect size d
*p* p value for the two group comparison
*t* t value for the two group comparison
*N* total N
*v* variance for the effect size
*se* standard error for the effect size
*pow* power given the true effect for the two group comparison
*n1* experimental group sample size
*n2* control group sample size

##**inspectMA** 
*d.obs* estimated coefficents of the model
*se.obs* standerd error of the estimate of the overall mean
*d.p* if the observed effect sizes are significantly different?
*mod.b.obs.#* estimated coefficents of the moderator (if dummy codes: difference between one group mean vs. comparison group mean; if contrast codes: difference between one group mean vs. grand average)
*mod.p.#* significance value for the moderation test, significance indicates moderator coefficient unusual for chance
*d.obs.pet* bias-adjusted PET estimate for delta
*p.pet* significance value for the PET estimate, significance indicates bias-adjusted estimate larger than chance
*b.egger* Egger coefficient for relationship between effect size and standard error
*p.egger* significance value for the egger test, significance indicates small-study effects possibly caused by bias
*joint.add.b#* PET-RMA (id+se) adjusted coefficients (grand mean & cell deviations OR cornerstone mean & cell deviations)
*joint.add.b.egger* coefficient of predictor 'se'
*joint.add.p#* significance value for coefficents for the PET-RMA (id+se) test, significance indicates significant bias-adjusted grand mean and/or differences between bias-adjusted subgroup means
*joint.add.p.egger* significance value for the additive effect of the PET-RMA (id+se) test, significance indicates overall small-study effect
*joint.inter.b#* PET-RMA (id*se) adjusted coefficients (grand mean & cell deviations OR cornerstone mean & cell deviations)
*joint.inter.b#.egger* Egger slopes (grand slope & subgroup differences in slope OR cornerstone slope & subgroup differences in slope)
*joint.inter.p#* significance value of the PET-RMA (id*se) adjusted estimates. Significance indicates moderation between bias-adjusted cell means.
*joint.inter.p#.egger* significance value of the interaction for the PET-RMA (id*se) test, significance indicates overall small-study effect or subgroup differences in small-study effects


####*Simulate a meta-analytic dataset with dataMA()*

*Basic Model*
```{r}
#create data
basic.data = dataMA(k = 10, delta = .2, tau = 0, 
               empN = 0, maxN = 200, minN = 20, meanN = 50, 
               selProp = 0, qrpEnv = "none", empN.boost = 0)


#Simulate
basic = rma(yi = d, sei = se, data = basic.data)
#View
summary(basic)
funnel(basic)
forest(basic)
funnel(trimfill(basic))
funnel(basic, level=c(90, 95, 99),
        shade = c("white", "grey75", "grey60"), refline=0)

```

*Null Model*
```{r}
null.data = dataMA(k = 100, delta = 0, tau = 0, 
               empN = 0, maxN = 200, minN = 20, meanN = 50, 
               selProp = 0, qrpEnv = "none", empN.boost = 0)

null = rma(yi = d, sei = se, data = null.data)

summary(null)
funnel(null, level=c(90, 95, 99),
        shade = c("white", "grey75", "grey60"), refline=0)
forest(null)

```

*Bias Model*
*k* the number of studies in the MA
*delta* the true effect (or the average of the true effects if heterogeneity exists)
*tau* the SD around the true effect
*empN* a logical, whether to use the empirical per-group N distribution
*maxN* the max possible group size that could be created *this needs to be set higher than what can actually be generated--it doesn't mean you get bigger samples
*minN* the min of the truncated normal for sample size
*meanN* the average of the truncated normal for sample size

*selProp* the proportion of the sample affected by bias
*qrpEnv* the qrp environment that produced the literature: 'none', 'low', 'med', 'high'
*empN.boost* A constant that is added to the empirical effect sizes
```{r}
selProp.data = dataMA(k = 100, delta = 0, tau = 0, 
               empN = 0, maxN = 200, minN = 20, meanN = 50, 
               selProp = .50, qrpEnv = "none", empN.boost = 0)
selProp1 = rma(yi = d, sei = se, data = selProp.data)

qrpEnv.data = dataMA(k = 100, delta = 0, tau = 0, 
               empN = 0, maxN = 200, minN = 20, meanN = 50, 
               selProp = 0, qrpEnv = "high", empN.boost = 0)
qrpEnv1 = rma(yi = d, sei = se, data = qrpEnv.data)

empN.boost.data = dataMA(k = 100, delta = 0, tau = 0, 
               empN = 0, maxN = 200, minN = 20, meanN = 50, 
               selProp = 0, qrpEnv = "none", empN.boost = .5)
empN.boost1 = rma(yi = d, sei = se, data = empN.boost.data)


funnel(selProp1, level=c(90, 95, 99),
        shade = c("white", "grey75", "grey60"), refline=0, main = "selProp1")
funnel(qrpEnv1, level=c(90, 95, 99),
        shade = c("white", "grey75", "grey60"), refline=0, main = "qrpEvn1")
funnel(empN.boost1, level=c(90, 95, 99),
        shade = c("white", "grey75", "grey60"), refline=0, main = "empN.boost1")


```


*Simulate a moderator effect (meta-regression)*
```{r}
dat <- dataMA(k = 10, delta = .2, tau = 0, 
               empN = 0, maxN = 200, minN = 20, meanN = 50, 
               selProp = 0, qrpEnv = "none", empN.boost = 0)

dat.mod <- data.frame(dat, "mod" = runif(50))
ma5 = rma(yi = d, sei = se, data = dat.mod,
          mods = mod)
summary(ma5)
plot(ma5)

```

